---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# strength

<!-- badges: start -->
<!-- badges: end -->

{strength} is a collection of computations related to strength training.  Currently this covers mapping between rating of perceived exertion (`rpe`), repetitions performed in a set (`reps`) and percentage of one rep max (`pct_1rm`).  If you have two (for example, RPE and reps), functions exist to compute the third (`pct_1rm` in this example).

## Installation

You can install the development version of strength from [GitHub](https://github.com/) with:

``` r
# install.packages('remotes')
remotes::install_github("alexpaynter/strength")
```

## Basic use

The following example calculates the estimated percentage of one rep max associated with 4 sets where reps and RPE were recorded:

```{r example}
library(strength)
library(tidyr)
tidyr::expand_grid(
  reps = c(3,10),
  rpe = c(8.5, 7)
) |>
  dplyr::mutate(pct_1rm = pct1rm_rts(reps = reps, rpe = rpe))
```

